\chapter{Conclusion}
\begin{spacing}{1.5}
Web is increasingly getting complex these days. Thousands of services spwan millions of requests each day. This work envisioned a intelligent web framework in which a service can create interconnections between diffrents services compatible. It opens up a multitude of possibilities, including a higher layer maniputation of information for what it represents than how it is represented.

Popularisation of services like ifttt have given us the proof that this service is inevitable in the future of web, and if machines were able to parse the information constituded by entire internet it can do wonders that no one envisioned, so it can only be comapred with magic.

The prototype mashup editor created can intelligintly mash the services based on annotoations But it is also limited in some aspects. But we hope this  direction deserves more exploration since it is relativly easy for the developer and the machine to follow. The prototype was implimented in different paradigms to verify the computatuiional completetability.

The imeediate future directions we would like to purse this works are
\begin{enumerate}
\item Change to accomodate todays REST APIs. Most of the rest apis in use today does to conform to the RESTful paradigm. They uses GET heavily to get most of the things done for perfomance purposes. This have to taken care of.

\item A tool to convert exishting REST APIs.
But this comes with lot of challenge. The above one for a start, adoption is another problem.
\end{enumerate}
\end{spacing}